Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2025-05-12 autovi_paper.qmd
Add one sentence to explain attention map
Refine the pkg extension part

The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`). This is achieved by substituting the relevant overridable modules, as illustrated in @fig-autovi-diag.

@@

It is important to note, however, that the pre-trained computer vision model was developed specifically for diagnostic evaluation of linear regression. Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature. If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised. For further discussion on extending the methodology to other model classes, refer to @li2024automated.

@@

The density plot in @fig-autovi-web-distributions offers a more robust result, allowing the user to compare the distribution of bootstrapped VSS with the distribution of null VSS. Finally, the grayscale attention map (right image) can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment.

>>>>

The `autovi` R package can be extended to accommodate other classes of models beyond linear regression, such as generalized linear models (`glm`). This is achieved by substituting the relevant overridable modules, and if needed, supplying a different `Keras` model.

@@

It is important to note, however, that the pre-trained computer vision model included in `autovi`, such as `vss_phn_32` (see `list_keras_models()` for the full list of available models), was developed specifically for diagnostics of linear regression. Its applicability to other model classes relies on the assumption that the null residual plots exhibit characteristics broadly consistent with those of well-behaved linear regression residuals, that is, residuals should be approximately randomly scattered around zero, display roughly constant variance across the range of fitted values, and exhibit no discernible structure or curvature. If these conditions are not met, or if model violations do not give rise to visually detectable patterns, the validity of the automated diagnostics may be compromised. In such cases, users are encouraged to train and apply their own `Keras` models. Detailed guidance on model training and discussion on extending the methodology to other model classes can be found in @li2024automated.

@@

The density plot in @fig-autovi-web-distributions offers a more robust result, allowing the user to compare the distribution of bootstrapped VSS with the distribution of null VSS. Finally, the grayscale attention map (right image) can be used to check if the target visual features, like the non-linearity present in the lineup example, are captured by the computer vision model, ensuring the quality of the assessment. The attention map is the gradient of the model output with respect to the grayscale image input, indicating the sensitivity of the output to each pixel.

### 2025-05-12 autovi_paper.tex
Add one sentence to explain attention map
Refine the pkg extension part

The \texttt{autovi} R package can be extended to accommodate other
classes of models beyond linear regression, such as generalized linear
models (\texttt{glm}). This is achieved by substituting the relevant
overridable modules, as illustrated in Figure~\ref{fig-autovi-diag}.

@@

It is important to note, however, that the pre-trained computer vision
model was developed specifically for diagnostic evaluation of linear
regression. Its applicability to other model classes relies on the
assumption that the null residual plots exhibit characteristics broadly
consistent with those of well-behaved linear regression residuals, that
is, residuals should be approximately randomly scattered around zero,
display roughly constant variance across the range of fitted values, and
exhibit no discernible structure or curvature. If these conditions are
not met, or if model violations do not give rise to visually detectable
patterns, the validity of the automated diagnostics may be compromised.
For further discussion on extending the methodology to other model
classes, refer to \citet{li2024automated}.

@@

The density plot in Figure~\ref{fig-autovi-web-distributions} offers a
more robust result, allowing the user to compare the distribution of
bootstrapped VSS with the distribution of null VSS. Finally, the
grayscale attention map (right image) can be used to check if the target
visual features, like the non-linearity present in the lineup example,
are captured by the computer vision model, ensuring the quality of the
assessment.

>>>>

The \texttt{autovi} R package can be extended to accommodate other
classes of models beyond linear regression, such as generalized linear
models (\texttt{glm}). This is achieved by substituting the relevant
overridable modules, and if needed, supplying a different \texttt{Keras}
model.

@@

It is important to note, however, that the pre-trained computer vision
model included in \texttt{autovi}, such as \texttt{vss\_phn\_32} (see
\texttt{list\_keras\_models()} for the full list of available models),
was developed specifically for diagnostics of linear regression. Its
applicability to other model classes relies on the assumption that the
null residual plots exhibit characteristics broadly consistent with
those of well-behaved linear regression residuals, that is, residuals
should be approximately randomly scattered around zero, display roughly
constant variance across the range of fitted values, and exhibit no
discernible structure or curvature. If these conditions are not met, or
if model violations do not give rise to visually detectable patterns,
the validity of the automated diagnostics may be compromised. In such
cases, users are encouraged to train and apply their own \texttt{Keras}
models. Detailed guidance on model training and discussion on extending
the methodology to other model classes can be found in
\citet{li2024automated}.

@@

The density plot in Figure~\ref{fig-autovi-web-distributions} offers a
more robust result, allowing the user to compare the distribution of
bootstrapped VSS with the distribution of null VSS. Finally, the
grayscale attention map (right image) can be used to check if the target
visual features, like the non-linearity present in the lineup example,
are captured by the computer vision model, ensuring the quality of the
assessment. The attention map is the gradient of the model output with
respect to the grayscale image input, indicating the sensitivity of the
output to each pixel.
